Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-13 dissemination.publication/9375838469ad4029/paper.tex
added ISBN
minor clean up

% ISBN
%\acmISBN{123-4567-24-567/08/06}

@@

  during first execution other missing soft dependencies will be detected or installed including libdma.so and VTA server

@@

$ ck install package:lib-nnvm-master --env.PACKAGE_URL=https://github.com/tqchen/nnvm --env.PACKAGE_GIT_CHECKOUT=qt

>>>>

% ISBN
\acmISBN{978-1-4503-5923-8}

@@

  during first execution other missing soft dependencies 
  will be detected or installed including libdma.so and VTA server.

@@

$ ck install package:lib-nnvm-master --env.PACKAGE_URL=https://github.com/tqchen/nnvm \
    --env.PACKAGE_GIT_CHECKOUT=qt
